\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-24 paper/subdocuments/results.Rnw

>>>>

# Variante mit Log

density1 <- density(log(bd.2003.ind$inc))
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "log(taxable income)", ylab = "density",
     axes = FALSE,
     xlim = c(-8, 10),
     ylim=c(0,0.5655167))
title(main="2003 vs 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(0,0),y=c(0.5655167,0.5655167))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("2003","2010"))
density2 <- density(log(bd.2010.ind$inc))
lines(x = (density2$x), y = density2$y, type = "l",lty=2)
